\documentclass[a4paper]{article} 
\usepackage[english]{babel} 
\usepackage[utf8x]{inputenc} 
\usepackage[T1]{fontenc} 
\usepackage{ragged2e} 
\usepackage{amsmath} 
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry} 
\begin{document} 
\section*{Index} 
\allowdisplaybreaks 
\begin{align*} 
&\text{Abelian groups} \thinmuskip&& vol. 1: p. 24\\
&\text{Adjoint operators} \thinmuskip&& vol. 1: pp. 43-44\\
&\text{Autonomous systems} \thinmuskip&& vol. 1: p. 7\\
&\text{Bifurcation} \thinmuskip&& vol. 1: pp. 11-12, 63-64\\
&\text{Body velocity} \thinmuskip&& vol. 1: p. 38\\
&\text{Centroid of area} \thinmuskip&& vol. 1: pp. 4-6\\
&\text{Cross product} \thinmuskip&& vol. 1: pp. 1-2\\
&\text{Dan} \thinmuskip&& vol. 1: p. 1\\
&\text{Degrees of freedom} \thinmuskip&& vol. 1: p. 17\\
&\text{Diffeomorphic} \thinmuskip&& vol. 1: p. 20\\
&\text{Direct product of two sets} \thinmuskip&& vol. 1: p. 20\\
&\text{Existence and uniqueness theorem} \thinmuskip&& vol. 1: pp. 11, 13\\
&\text{Exponential map} \thinmuskip&& vol. 1: pp. 48-51\\
&\text{External forces} \thinmuskip&& vol. 1: p. 1\\
&\text{Force couple} \thinmuskip&& vol. 1: p. 2\\
&\text{Force couple system} \thinmuskip&& vol. 1: p. 3\\
&\text{Forward kinematics} \thinmuskip&& vol. 1: p. 78\\
&\text{Generalized coordinates} \thinmuskip&& vol. 1: p. 78\\
&\text{Geodesics} \thinmuskip&& vol. 1: pp. 44-46, 51\\
&\text{Group} \thinmuskip&& vol. 1: p. 21\\
&\text{Group, left/right action} \thinmuskip&& vol. 1: pp. 24-29, 33-33, 80\\
&\text{Holonomic constraint} \thinmuskip&& vol. 1: pp. 76-77\\
&\text{Homeomorphic} \thinmuskip&& vol. 1: p. 19\\
&\text{Hysteresis} \thinmuskip&& vol. 1: pp. 66, 70-71\\
&\text{Internal forces} \thinmuskip&& vol. 1: p. 1\\
&\text{Isomorphic} \thinmuskip&& vol. 1: p. 22\\
&\text{Lie algebra} \thinmuskip&& vol. 1: p. 41\\
&\text{Lie groups} \thinmuskip&& vol. 1: p. 21\\
&\text{Lifted actions} \thinmuskip&& vol. 1: pp. 31-34\\
&\text{Linearization at a fixed point} \thinmuskip&& vol. 1: pp. 10-11\\
&\text{Manifolds} \thinmuskip&& vol. 1: pp. 17-19\\
&\text{Manifolds, accessible} \thinmuskip&& vol. 1: pp. 76-78\\
&\text{Manifolds, c$^k$-differentiable} \thinmuskip&& vol. 1: p. 20\\
&\text{Modular addition} \thinmuskip&& vol. 1: p. 21\\
&\text{Monotonic function} \thinmuskip&& vol. 1: p. 13\\
&\text{Multiplicative calculus} \thinmuskip&& vol. 1: pp. 34-38, 46-47\\
&\text{Phase portrait} \thinmuskip&& vol. 1: pp. 7-9\\
&\text{Potentials} \thinmuskip&& vol. 1: p. 17\\
&\text{Reaction force} \thinmuskip&& vol. 1: p. 4\\
&\text{Rigid body} \thinmuskip&& vol. 1: p. 23\\
&\text{Rigid body, left lifted action} \thinmuskip&& vol. 1: pp. 38-41\\
&\text{Rigid body, right lifted action} \thinmuskip&& vol. 1: pp. 41-43\\
&\text{Semidirect product of two sets} \thinmuskip&& vol. 1: p. 24\\
&\text{Spatial velocity} \thinmuskip&& vol. 1: p. 43\\
&\text{Special euclidean group} \thinmuskip&& vol. 1: p. 23\\
&\text{Special orthogonal group, \emph{so(n)}} \thinmuskip&& vol. 1: p. 22\\
&\text{Tangent spaces} \thinmuskip&& vol. 1: pp. 29-30\\
&\text{Varignon's theorem} \thinmuskip&& vol. 1: p. 1\\
&\text{Vector field} \thinmuskip&& vol. 1: pp. 30-31\\
&\text{Zero set} \thinmuskip&& vol. 1: p. 76\\
\end{align*} 
\end{document}